---
title: "Data ggplot1"
author: "Yifan Su"
date: "10/2/2020"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

```{r message = FALSE, warning = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), # temperature min and max
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```


## Scatterplots!!

Create my first scatterplot ever.

```{r message = FALSE, warning = FALSE}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

New apprache, same plot.

```{r message = FALSE, warning = FALSE}
weather_df %>%  # do this to mutate or filter smthing
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object.

```{r message = FALSE, warning = FALSE}
weather_plot =
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot = geom_point()
```

## Advanced scatterplot ...

Start with the same one and make it fancy!

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE) # standard errors
```

What about the `aes` placement ...?

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + #statics
  geom_point(aes(color = name)) + #color only applied to the scatterplot
  geom_smooth()
```

Let's facet some thing!!

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) +
  geom_point(alpha = .2, size = .3) + 
  geom_smooth(se = FALSE) + # standard errors
facet_grid(. ~ name) # ignor row, create the colomns
```

Let's combine some elements and try a new plot.

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) + #add precipitation
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


## Some small notes

How many geoms have to exist?

You can have whatever geoms you want.

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom!

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex() + #package `hexbin` required for `stat_binhex`
  geom_bin2d() + 
  geom_density2d() #地形图
```

## Univariate plots

Histograms are really great.

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color ..

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge") + # make it more slim
  facet_grid(. ~ name)
```

Let's try a new geometry!

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3, adjust = .5) #histogram but smooth, loose a little info/ adjust=add some peak
```

What about box plots?

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```

Trendy plots ;-)

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin(alpha = .5) +#boxplot likes a violin
  stat_summary(fun = "median")
```

Ridge plots -- the most popular plot of 2017

```{r message = FALSE, warning = FALSE}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) + 
  geom_density_ridges() # separate = like states
```



## Save and Embed

Let's save a scatterplot.

```{r}
weather_plot =
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("weather_plot.pdf", weather_plot, width =  8, height = 5)
```

What about embeding ..

```{r, fig.width=6, fig.height=3}
weather_plot
```

Embed at different size.

```{r, fig.width=12, fig.height=6}
weather_plot
```





